Deep mutational scanning of hemagglutinin helps distinguish the evolutionary fate of human H3N2 influenza virus lineages

### 2018-01-04 paper/manuscript.tex
Change coloring of mut tolerance heatmaps
Added small details to FigS1 caption

\begin{figure*}
\centering
\includegraphics[width=16cm]{figs/mut_tolerance/entropy_heatmap.pdf}
\caption{\label{fig:mut_tolerance}
{\bf Mutational tolerance mapped onto each site of HA.}
Mutational tolerance as calculated by the Shannon entropy of a given site's amino-acid preferences are mapped onto the structure of the H3 trimer (PDB 4O5N;~\cite{lee2014receptor}) and the H1 trimer (PDB 1RVX;~\cite{gamblin2004structure}), with both trimers in approximately the same orientation. 
The site entropies were calculated from the preferences measured in the Perth/2009 H3 (left panel) from this study, or the preferences measured in the WSN/1933 H1 (right panel) from~\cite{doud2016accurate}. 
Lighter shades of blue or red signify low mutational tolerance, while darker shades of blue or red signify high mutational tolerance. 
For each HA, the structure on the left side colors the full HA trimer, while the structure on the right side colors only one of the monomers.
The sialic acid receptor is shown as black sticks.
The Perth/2009 H3 shows relatively high mutational tolerance in the stalk region, particularly in helix A, compared to the head region. 
High mutational tolerance in H3 was also observed near antigenic site C and near the 190 helix.
The head region of the WSN/1933 H1 is mutationally tolerant compared to the relatively intolerant stalk region. 
}
\end{figure*}

@@

\begin{suppfigure}
\centerline{\includegraphics[width=0.5\textwidth]{figs/S01_G78D-T212I/G78D-T212I.pdf}}
\caption{\label{suppfig:Perth2009_mut}
{\bf Characterization of the G78D-T212I Perth/2009 HA variant.} 
(A) 
The G78D-T212I Perth/2009 HA variant grows to higher titers than do viruses carrying the wildtype Perth/2009 HA.
Each virus was generated in duplicate by reverse genetics and passaged once at MOI = 0.01 in MDCK-SIAT1-TMPRSS2 cells.
The rescue and passage viral supernatants were collected at 72 hours post-transfection and 44 hours post-infection, respectively, and titered in MDCK-SIAT1-TMPRSS2 cells. 
The points mark each duplicate and the bar marks the mean.
(B)
The D78 variant remained at a low frequency in natural human H3N2 sequences over the past $~\sim$10 years.
The A212 variant rose to fixation in $~\sim$2011, replacing the T212 variant.
}
\end{suppfigure}

>>>>

\begin{figure*}
\centering
\includegraphics[width=16cm]{figs/mut_tolerance/entropy_heatmap.pdf}
\caption{\label{fig:mut_tolerance}
{\bf Mutational tolerance mapped onto each site of HA.}
Mutational tolerance as calculated by the Shannon entropy of a given site's amino-acid preferences are mapped onto the structure of the H3 trimer (PDB 4O5N;~\cite{lee2014receptor}) and the H1 trimer (PDB 1RVX;~\cite{gamblin2004structure}), with both trimers in approximately the same orientation. 
The site entropies were calculated from the preferences measured in the Perth/2009 H3 (left panel) from this study, or the preferences measured in the WSN/1933 H1 (right panel) from~\cite{doud2016accurate}. 
Lighter shades of purple or brown signify low mutational tolerance, while darker shades signify high mutational tolerance. 
For each HA, the structure on the left side colors the full HA trimer, while the structure on the right side colors only one of the monomers.
The sialic acid receptor is shown as black sticks.
The Perth/2009 H3 shows relatively high mutational tolerance in the stalk region, particularly in helix A, compared to the head region. 
High mutational tolerance in H3 was also observed near antigenic site C and near the 190 helix.
The head region of the WSN/1933 H1 is mutationally tolerant compared to the relatively intolerant stalk region. 
}
\end{figure*}

@@

\begin{suppfigure}
\centerline{\includegraphics[width=0.5\textwidth]{figs/S01_G78D-T212I/G78D-T212I.pdf}}
\caption{\label{suppfig:Perth2009_mut}
{\bf Characterization of the G78D-T212I Perth/2009 HA variant.} 
(A) 
The G78D-T212I Perth/2009 HA variant supports better viral growth than the wildtype Perth/2009 HA.
Viruses were generated in duplicate by reverse genetics with the Perth/2009 NA and WSN internal genes, and passaged once at MOI = 0.01 in MDCK-SIAT1-TMPRSS2 cells.
The rescue and passage viral supernatants were collected at 72 hours post-transfection and 44 hours post-infection, respectively, and titered in MDCK-SIAT1-TMPRSS2 cells. 
The points mark each duplicate and the bar marks the mean.
(B)
The D78 variant remained at a low frequency in natural human H3N2 sequences over the past $~\sim$10 years.
The A212 variant rose to fixation in $~\sim$2011, replacing the T212 variant.
}
\end{suppfigure}
